---
output: 
  html_document:
    theme: flatly
---

# “Look at them, they are idiots lol”: Partisan Social Media Influencers, Disparagement Humor, and Audience Reaction Dynamics on TikTok

## Description

This is the analysis code for the study *“Look at them, they are idiots lol”: Partisan Social Media Influencers, Disparagement Humor, and Audience Reaction Dynamics on TikTok*. You need to have correct `.env` file specifying the working directory. Additionally, you require correct dataset being pre-processed (e.g., sentiment annotations). If everything is correctly set up, the code will run without any interruption. You can also knit this markdown and get an output as a single HTML file. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(anytime)
library(readr)
library(ggplot2)
library(lme4)
library(glmmTMB)
library(performance)
library(interactions)
library(patchwork)
library(DHARMa)
library(sjPlot)
library(car)
library(emmeans)
library(dotenv)
library(scales)

load_dot_env("../.env")
Data_Storage <- Sys.getenv("DATA_STORAGE")

```

## Load & Process Data
```{r}

# Gets all the batches of comment data
file_list <- list.files(path=file.path(Data_Storage, "roberta_annotated"), full.names = TRUE)
# remove validation data path
file_list <- file_list[!grepl("/sampled_", file_list)] 
# bind all the comments together
df_comment <- file_list %>% 
  lapply(read_csv, col_types = cols(id = col_character(), parent_comment_id = col_character(), video_id = col_character())) %>% 
  bind_rows()

# de-duplication of comments (for some reason, many duplication were detected)
df_comment <- df_comment %>%
  distinct(video_url, id, text, .keep_all = TRUE)

# Removing replies (although no child comments are collected from TikTok API)
df_comment <- df_comment %>% 
  filter(parent_comment_id == video_id)

# save de-duplicated comment
write.csv(df_comment, file.path(Data_Storage, "clean_20241001_20241130_comments_data.csv"))

# load video data
df_video <- read.csv(file.path(Data_Storage, "20241001_20241130_video_data_coding.csv"))

# Total number of extracted videos
dim(df_video)

# Data formatting
df_video <- df_video %>%
  # removing non-partisan SMI = @philipdefranco
  filter(username != "philipdefranco") %>% 
  # Assigning partisan labels
  mutate(Partisanship = case_when(
    username %in% c("aaronparnas1", "briantylercohen", "davidpakmanshow", "harryjsisson", "joyreidofficial", "rbreich", "tizzyent", "underthedesknews") ~ as.factor("Democratic"),
    TRUE ~ as.factor("Republican")
  )) %>%
  # changing data type from chr to factor
  mutate(Disparagement = as.factor(Disparagement)) %>% 
  # adding number of follower information, unit is kilo
  mutate(num_followers = case_when(
    username == "aaronparnas1" ~ 4800,
    username == "briantylercohen" ~ 1100, 
    username == "davidpakmanshow" ~ 1300,
    username == "harryjsisson" ~ 2100, 
    username == "joyreidofficial" ~ 869.7, 
    username == "rbreich" ~ 1300, 
    username == "tizzyent" ~ 7900, 
    username == "underthedesknews" ~ 3700,
    username == "adamcalhoun1" ~ 3000, 
    username == "danbongino" ~ 640.3, 
    username == "candaceoshow" ~ 6400, 
    username == "daterightstuff" ~ 3200, 
    username == "patrickbetdavid" ~ 1500, 
    username == "real.benshapiro" ~ 2900, 
    username == "the_jefferymead" ~ 2100, 
    username == "thecharliekirkshow" ~ 9500, 
    username == "thecommentssection" ~ 1700, 
    username == "theofficertatum" ~ 1600, 
    username == "tuckercarlson" ~ 3100
  )) %>% 
  # replacing the number of comments 0 to NA for the video with a closed comment section
  mutate(comment_count = case_when(
    video_url == "https://www.tiktok.com/@underthedesknews/video/7435498266365594911" ~ NA_real_,
    TRUE ~ comment_count
  )) %>% 
  # changes made after intra-coder reliability check
  mutate(Disparagement = case_when(
    video_url == "https://www.tiktok.com/@real.benshapiro/video/7424214695730597151" ~ "1",
    video_url == "https://www.tiktok.com/@tizzyent/video/7422383813440949534" ~ "1",
    TRUE ~ Disparagement
  ))

# Descriptive statistics 
## Overall
df_video %>% 
  pull(Political) %>% 
  table()

df_video %>% 
  pull(Disparagement) %>% 
  table()

# per SMI for display
df_description <- df_video %>% 
  group_by(username) %>% 
  summarise(
    disparagement_1 = sum(Disparagement == 1),
    disparagement_1_prop = disparagement_1/n(),
    disparagement_0 = sum(Disparagement == 0 & Political == 1),
    disparagement_0_prop = disparagement_0/n(),
    political_0 = sum(Political == 0),
    political_0_prop = political_0/n(),
    na = sum(Political == "n/a"),
    na_prop = na/n(),
    total_n = n()
  ) %>% 
  arrange(desc(disparagement_1_prop))

# show descriptive statistics
tab_df(df_description)

# Filter only Political videos
df_video <- df_video %>% 
  filter(Political == "1")

```

## Model Choice & Descriptive Statistics
```{r}
df_video %>%
  summarize(across(
    c(view_count, like_count, share_count, comment_count),
    list(
      n = ~sum(!is.na(.)),
      mean = ~mean(., na.rm = TRUE),
      var = ~var(., na.rm = TRUE),
      sd = ~sd(., na.rm = TRUE)
    )
  ))

# Clearly, the result is variance > mean. 
# Therefore, negative binomial regression will be fitted when these engagement metrics are dependent Variables. 
# Additionally, when choosing the dispersion family in the glmmTMB function, nbinom2 is thus appropriate, as it can be used when there is strong overdispersion, like this case. 

# Welch Two Sample t-test to see num of follower difference across partisan camps
followers_df_partisanship <- df_video %>% 
  distinct(username, num_followers, Partisanship)
t.test(num_followers ~ Partisanship, data = followers_df_partisanship)

```

## Data Quality Checks
```{r, fig.width=12, fig.height=6}
# Number of comments extracted per video
extracted_comment_num <- df_comment %>% 
  group_by(video_url) %>% 
  count() %>% 
  ungroup() %>% 
  rename(extracted_comment_count = n)

df_video_realcomm_num <- df_video %>% 
  select(video_url, comment_count, username) %>% 
  left_join(extracted_comment_num, by = "video_url")

ggplot(df_video_realcomm_num, aes(comment_count, extracted_comment_count, colour = username)) + 
  geom_point() + 
  geom_abline(intercept = 0, slope = 1) + 
  geom_abline(intercept = 500, slope = 0) +
  coord_cartesian(xlim = c(0, 5000), ylim = c(0, 5000)) + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

ggplot(df_video_realcomm_num, aes(comment_count, extracted_comment_count, colour = username)) + 
  geom_point() + 
  geom_abline(intercept = 0, slope = 1) + 
  # geom_abline(intercept = 500, slope = 0) +
  coord_cartesian(xlim = c(0, 30000), ylim = c(0, 30000)) + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

df_video_realcomm_num %>% 
  filter(extracted_comment_count < 2500) %>% 
  ggplot(aes(extracted_comment_count)) + geom_histogram(binwidth = 100) + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

df_video_realcomm_num %>% 
  select(comment_count, extracted_comment_count) %>% 
  mutate(proportion = extracted_comment_count/comment_count * 100) %>% 
  ggplot(aes(proportion)) + geom_histogram(binwidth = 10) + 
  theme_minimal() 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

cor.test(df_video_realcomm_num$comment_count, df_video_realcomm_num$extracted_comment_count)


```

## Time lapse from video post to comment post
```{r}
# Select only required info
df_comment_longi <- df_comment %>%
  select(video_url, id, create_time) %>%
  rename(comment_create_time = create_time)

df_video_longi <- df_video %>%
  select(video_url, create_time) %>%
  rename(video_create_time = create_time)

video_comment_time_df <- left_join(df_video_longi, df_comment_longi, by = "video_url")

# calculate comment accumulation
df_cumulative <- video_comment_time_df %>%
  mutate(video_time_std = anytime(video_create_time),
         comment_time_std = anytime(comment_create_time)) %>%
  mutate(lapse = ceiling(as.numeric(difftime(comment_time_std, video_time_std, units = "mins"))))

df_comment <- left_join(df_comment, df_cumulative %>% select(video_url, id, lapse), by = c("video_url", "id"))

```

## Longitudinal Comment Growth

```{r}
df_cumulative <- df_cumulative %>%
  select(video_url, lapse) %>%
  filter(!is.na(lapse)) %>%
  group_by(video_url) %>%
  arrange(lapse, .by_group = TRUE) %>%
  mutate(
    cum_prop = row_number() / n()
  ) %>%
  summarise(
    exceed_0.3_min = lapse[which.max(cum_prop > 0.3)], # get the time (min) that accumulated comments exceeded 30% of the total comment
    exceed_0.5_min = lapse[which.max(cum_prop > 0.5)], # 50%
    exceed_0.7_min = lapse[which.max(cum_prop > 0.7)], # 70%
    exceed_0.9_min = lapse[which.max(cum_prop > 0.9)]  # 90%
  ) %>%
  ungroup()

df_exceed_all <- df_cumulative %>%
  pivot_longer(
    cols = c(exceed_0.3_min, exceed_0.5_min, exceed_0.7_min, exceed_0.9_min),
    names_to = "threshold",
    values_to = "value"
  ) %>%
  group_by(threshold, value) %>%
  summarise(freq = n(), .groups = "drop") %>%
  arrange(threshold, value) %>%
  group_by(threshold) %>%
  mutate(cum_prop = cumsum(freq) / sum(freq)) %>%
  ungroup()

time_labels <- function(x) {
  ifelse(
    x < 60,
    paste0(x, " min"),
    ifelse(
      x < 1440,
      paste0(round(x / 60, 1), " h"),
      paste0(round(x / 1440, 1), " D")
    )
  )
}

ggplot(df_exceed_all,
       aes(x = value, y = cum_prop, color = threshold)) +
  geom_line() +
  scale_x_log10(
    breaks = c(1, 10, 30, 60, 180, 600, 1440, 4320, 10080, 20160, 43200, 144000, 432000),
    labels = time_labels
  ) +
  labs(
    x = "Time from Post",
    y = "Cumulative proportion of videos exceeded Threshold",
    color = "Threshold"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

```

## Calculate Sentiment Polarization
```{r}
# calculating sentiment proportions per video ---------
sentiment_aggregation <- function(comment_data){
  comment_data %>% 
    group_by(username, video_url) %>% 
    count(sentiment_value) %>% 
    complete(sentiment_value = c("negative", "neutral", "positive"), fill = list(n = 0)) %>% 
    group_by(username, video_url) %>% 
    mutate(sentiment_proportion = n / sum(n))
}

sentiment_agg_df <- sentiment_aggregation(df_comment)
```

```{r}
# cumulative entropy calculation function
binary_entropy = function(p){
  if (is.na(p)){
    return(NA)
  }
  else if (p == 0 || p == 1) {
    return(0)
  }
  else{
    one_minus_p = 1 - p
    exponent = -(p*log(p, base = 2) + (one_minus_p*log(one_minus_p, base = 2)))
    2**exponent - 1
  }
}

cumulative_entropy = function(data){
  k_1 = length(data) - 1
  each_entropy_vector = c()
  for (j in seq(k_1)){
    S_j = sum(data[1:j])
    each_entropy = binary_entropy(S_j)
    each_entropy_vector <- c(each_entropy_vector, each_entropy)
  }
  mean(each_entropy_vector)
}

# # Examples
# cumulative_entropy(c(0.1, 0.2, 0.2, 0.2, 0.2, 0.1))
# # [1] 0.6904673
# cumulative_entropy(c(0.1, 0.8, 0.1))
# # [1] 0.3841455

```

```{r}
# Example Plot
toy_1 <- c(0.1, 0.8, 0.1)
toy_2 <- c(0.2, 0.6, 0.2)
toy_3 <- c(0.3, 0.4, 0.3)
toy_4 <- c(0.4, 0.2, 0.4)
toy_5 <- c(0.5, 0.0, 0.5)
toy_6 <- c(0.1, 0.3, 0.6)
toy_7 <- c(0.0, 0.3, 0.7)
toy_8 <- c(0.0, 0.5, 0.5)
toy_9 <- c(0.0, 0.7, 0.3)

toy_visualization <- function(vector_data){
  score <- cumulative_entropy(vector_data) %>% 
    round(digits = 2)
  
  df <- data.frame(
    label = c("negative", "neutral", "positive"), 
    value = vector_data
    )

  # Plot
  ggplot(df, aes(x = label, y = value)) +
    geom_bar(stat = "identity", fill = "#00BFC4") +
    annotate("text", x = Inf, y = Inf, label = score,
           hjust = 1.1, vjust = 1.56, size = 6) +
    theme_minimal() +
    coord_cartesian(ylim = c(0, 1))
  }

p_toy_1 <- toy_visualization(toy_1)
p_toy_2 <- toy_visualization(toy_2)
p_toy_3 <- toy_visualization(toy_3)
p_toy_4 <- toy_visualization(toy_4)
p_toy_5 <- toy_visualization(toy_5)
p_toy_6 <- toy_visualization(toy_6)
p_toy_7 <- toy_visualization(toy_7)
p_toy_8 <- toy_visualization(toy_8)
p_toy_9 <- toy_visualization(toy_9)

(p_toy_1 + p_toy_2 + p_toy_3 + p_toy_4 + p_toy_5 + p_toy_6 + p_toy_7 + p_toy_8 + p_toy_9) +
  plot_layout(guides = "collect") &
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())


```

```{r}
# calculating sentiment polarization score per video 
polarization_calculation <- function(aggregated_comment_sentiment_data){
  aggregated_comment_sentiment_data %>% 
    group_by(username, video_url) %>% 
    mutate(polarization_score = cumulative_entropy(sentiment_proportion)) %>% 
    pivot_wider(
      id_cols = c(video_url, username, polarization_score),
      names_from = sentiment_value, 
      values_from = c(n, sentiment_proportion),
      names_glue = "{sentiment_value}_{.value}"
    ) %>% 
    rowwise() %>%
    mutate(sum = sum(negative_n, neutral_n, positive_n, na.rm = T)) %>% 
    ungroup()
}

polarization_agg_df <- polarization_calculation(sentiment_agg_df)


# 
# # Creating and calculating longtitudional data
# longitudinal_data <- map_dfr(1:24, function(hour) {
#   threshold_lapse <- hour * 60
# 
#   df_comment %>%
#     filter(lapse <= threshold_lapse) %>%
#     sentiment_aggregation() %>%
#     polarization_calculation() %>%
#     mutate(time = hour)
# })
# 
# longitudinal_data_completed <- longitudinal_data %>%
#   group_by(video_url, username) %>%
#   complete(
#     time = 1:24,
#     fill = list(polarization_score = NA_real_, negative_n = 0, neutral_n = 0, positive_n = 0, negative_sentiment_proportion = NA_real_, neutral_sentiment_proportion = NA_real_, positive_sentiment_proportion = NA_real_, sum = 0))
# 

```

```{r}
# merge it back to video_data
final_df <- left_join(df_video, polarization_agg_df, by = c("video_url", "username"))

# write it to csv file to be safe
write.csv(final_df, file.path(Data_Storage, "20241001_20241130_video_data_with_pol_score.csv"))

df_video <- final_df

df_video$Disparagement <- factor(
  df_video$Disparagement,
  levels = c(0, 1),
  labels = c("Non-disparagement", "Disparagement")
)

# Descriptive analysis of sentiment polarization
df_video %>% 
  select(polarization_score) %>% 
  summarize(n = n(),
            na = sum(is.na(polarization_score)), 
            m = mean(polarization_score, na.rm = TRUE), 
            sd = sd(polarization_score, na.rm = TRUE))

# Descriptive statistics of comments (only comments attached to the included videos)
df_video %>% 
  pull(sum) %>% 
  sum(na.rm = TRUE)

df_video %>% 
  select(sum) %>% 
  summarize(m = mean(sum, na.rm = TRUE), 
            sd = sd(sum, na.rm = TRUE))
  

```

## RQ1 Descriptive Analysis
```{r}
# Changing data type to numeric one, and subtract 1 so that values become 0 and 1, not 1 and 2 ---------
df_descriptive <- df_video %>% 
  mutate(Disparagement = as.numeric(Disparagement) - 1)

# Political video's stats
df_video %>%
  count(username) %>%
  summarise(mean = mean(n), sd = sd(n))

# Disparagement proportion stats
df_descriptive %>% 
  select(Disparagement) %>% 
  summarize(mean = mean(Disparagement))

# Disparagement count and count per partisan SMI stats
df_descriptive %>%
  group_by(username) %>% 
  summarize(N = sum(Disparagement), .groups = 'drop') %>% 
  summarise(Total = sum(N), mean = mean(N), sd = sd(N))
  
# Per Partisanship stats
df_descriptive <- df_descriptive %>% 
  group_by(Partisanship, username) %>% 
  summarize(disparagement_prop = mean(Disparagement, na.rm = TRUE), 
            N_all = n(), 
            N_disparagement = sum(Disparagement))

df_descriptive %>% 
  group_by(Partisanship) %>% 
  summarize(Mean = mean(disparagement_prop, na.rm = TRUE), 
            SD = sd(disparagement_prop, na.rm = TRUE))

# Welch Two Sample t-test to see inter-partisan difference
t.test(disparagement_prop ~ Partisanship, data = df_descriptive)

```
## Multilevel Regression Model Fit (null-model)
```{r}
## num of view
null_model_view <- glmmTMB(view_count ~ 1 + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of likes
null_model_like <- glmmTMB(like_count ~ 1 + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of shares
null_model_share <- glmmTMB(share_count ~ 1 + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of comments
null_model_comment <- glmmTMB(comment_count ~ 1 + (1 | username), data = df_video, family = nbinom2(link = "log"))

# Output
tab_model(null_model_view, null_model_like, null_model_share, null_model_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

## sentiment polarization
null_model_polarization <- lmer(polarization_score ~ 1 + (1 | username), data = df_video)

# Output
tab_model(null_model_polarization, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Sentiment Polarization"), 
          show.ci = FALSE, 
          show.se = TRUE)

```


## H1 (disparagement -> engagement)

```{r}
## num of view
h1_model_view <- glmmTMB(view_count ~ Disparagement + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_h1_model_view <- simulateResiduals(h1_model_view)
# testDispersion(sim_res_h1_model_view)

## num of likes
h1_model_like <- glmmTMB(like_count ~ Disparagement + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_h1_model_like <- simulateResiduals(h1_model_like)
# testDispersion(sim_res_h1_model_like)

## num of shares
h1_model_share <- glmmTMB(share_count ~ Disparagement + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_h1_model_share <- simulateResiduals(h1_model_share)
# testDispersion(sim_res_h1_model_share)

## num of comments
h1_model_comment <- glmmTMB(comment_count ~ Disparagement + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_h1_model_comment <- simulateResiduals(h1_model_comment)
# testDispersion(sim_res_h1_model_comment)

# html output of the result ---------
tab_model(h1_model_view, h1_model_like, h1_model_share, h1_model_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

```

## H2 (disparagement -> polarization)

```{r}
h2_model <- lmer(polarization_score ~ Disparagement + (1 | username), data = df_video)
# sim_res_h2_model_like <- simulateResiduals(h2_model)
# testDispersion(sim_res_h2_model_like)
# summary(h2_model)

tab_model(h2_model, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Sentiment Polarization"), 
          show.ci = FALSE, 
          show.se = TRUE)

# visualization
df_sentiment_vis <- df_video %>% 
  # group_by(Disparagement) %>% 
  summarise(n=n(),
            agg_negative_proportion = mean(negative_sentiment_proportion, na.rm = TRUE), 
            agg_neutral_proportion = mean(neutral_sentiment_proportion, na.rm = TRUE), 
            agg_positive_proportion = mean(positive_sentiment_proportion, na.rm = TRUE), 
            
            agg_negative_sd = sd(negative_sentiment_proportion, na.rm = TRUE), 
            agg_neutral_sd = sd(neutral_sentiment_proportion, na.rm = TRUE), 
            agg_positive_sd = sd(positive_sentiment_proportion, na.rm = TRUE), 
            
            agg_negative_se = agg_negative_sd/sqrt(n), 
            agg_neutral_se = agg_neutral_sd/sqrt(n), 
            agg_positive_se = agg_positive_sd/sqrt(n)
            )

df_long_sentiment_vis <- df_sentiment_vis %>%
  pivot_longer(cols = matches("^agg_(negative|neutral|positive)_(proportion|se)$"),
               names_to = c("sentiment", ".value"), 
               names_pattern = "agg_(negative|neutral|positive)_(proportion|se)"
               )

ggplot(df_long_sentiment_vis, aes(x = sentiment, y = proportion)) +
  geom_col() +
  geom_col(fill = "#00BFC4") + 
  geom_errorbar(aes(ymin = proportion - se, ymax = proportion + se), width = 0.2) +
  labs(x = "Sentiment", y = "Proportion") +
  coord_cartesian(ylim = c(0, 1)) +
  theme_minimal()+ 
  theme(axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

```

## RQ2 (disparagement * polarization -> engagement & disparagement * engagement -> polarization)

```{r}
## num of view
rq2_model_view <- glmmTMB(view_count ~ Disparagement * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
rq2_model_view_no_interaction <- glmmTMB(view_count ~ Disparagement + polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
# summary(rq2_model_view)

## num of likes
rq2_model_like <- glmmTMB(like_count ~ Disparagement * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
rq2_model_like_no_interaction <- glmmTMB(like_count ~ Disparagement + polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
# summary(rq2_model_like)

## num of shares
rq2_model_share <- glmmTMB(share_count ~ Disparagement * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
rq2_model_share_no_interaction <- glmmTMB(share_count ~ Disparagement + polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
# summary(rq2_model_share)

## num of comments
rq2_model_comment <- glmmTMB(comment_count ~ Disparagement * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
rq2_model_comment_no_interaction <- glmmTMB(comment_count ~ Disparagement + polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))
# summary(rq2_model_comment)

## sentiment polarization, view
rq2_model_polarization_view <- lmer(polarization_score ~ Disparagement * log10(view_count) + (1 | username), data = df_video)
rq2_model_polarization_view_no_interaction <- lmer(polarization_score ~ Disparagement + log10(view_count) + (1 | username), data = df_video)
# summary(rq2_model_polarization_view)

## sentiment polarization, like
rq2_model_polarization_like <- lmer(polarization_score ~ Disparagement * log10(like_count) + (1 | username), data = df_video)
rq2_model_polarization_like_no_interaction <- lmer(polarization_score ~ Disparagement + log10(like_count) + (1 | username), data = df_video)
# summary(rq2_model_polarization_like)

## sentiment polarization, share
### log + 1 transformation
rq2_model_polarization_share <- lmer(polarization_score ~ Disparagement * log10(share_count + 1) + (1 | username), data = df_video)
rq2_model_polarization_share_no_interaction <- lmer(polarization_score ~ Disparagement + log10(share_count + 1) + (1 | username), data = df_video)
# summary(rq2_model_polarization_share)

## sentiment polarization, comment
### log + 1 transformation
rq2_model_polarization_comment <- lmer(polarization_score ~ Disparagement * log10(comment_count + 1) + (1 | username), data = df_video)
rq2_model_polarization_comment_no_interaction <- lmer(polarization_score ~ Disparagement + log10(comment_count + 1) + (1 | username), data = df_video)
# summary(rq2_model_polarization_comment)

# html output of the result ---------
tab_model(rq2_model_view, rq2_model_like, rq2_model_share, rq2_model_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

tab_model(rq2_model_polarization_view, rq2_model_polarization_like, rq2_model_polarization_share, rq2_model_polarization_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = "Polarization Score (engagement metrics log-transformed)", 
          show.ci = FALSE, 
          show.se = TRUE)

tab_model(rq2_model_view_no_interaction, rq2_model_like_no_interaction, rq2_model_share_no_interaction, rq2_model_comment_no_interaction,
          transform = NULL,
          auto.label = TRUE,
          collapse.ci = FALSE,
          dv.labels = c("Views", "Likes", "Shares", "Comments"),
          show.ci = FALSE,
          show.se = TRUE)

tab_model(rq2_model_polarization_view_no_interaction, rq2_model_polarization_like_no_interaction, rq2_model_polarization_share_no_interaction, rq2_model_polarization_comment_no_interaction,
          transform = NULL,
          auto.label = TRUE,
          collapse.ci = FALSE,
          dv.labels = "Polarization Score (engagement metrics log-transformed)",
          show.ci = FALSE,
          show.se = TRUE)


```

## RQ2 Vizualzation

```{r, fig.width=12, fig.height=6}
figure_for_rq2 <- function(regression_model, fig_num){
  plot_model(
    regression_model,
    type = "pred",
    terms = c("polarization_score", "Disparagement"),
    line.size = 1.5) +
    aes(linetype = group, colour = group) +
    scale_colour_manual(values = c("Non-disparagement" = "darkgreen", "Disparagement" = "purple")) +
    scale_fill_manual(values = c("Non-disparagement" = "darkgreen", "Disparagement" = "purple")) +
    scale_y_continuous(limits = c(0, NA)) +
    labs(title = fig_num, colour = "Disparagement", linetype = "Disparagement", shape = "Disparagement") +
    theme_minimal()
}

p_rq2_view <- figure_for_rq2(rq2_model_view, "A")
p_rq2_like <- figure_for_rq2(rq2_model_like, "B")
p_rq2_share <- figure_for_rq2(rq2_model_share, "C")
p_rq2_comment <- figure_for_rq2(rq2_model_comment, "D")

(p_rq2_view + p_rq2_like + p_rq2_share + p_rq2_comment) +
  plot_layout(guides = "collect") &
  theme(legend.position = "right",
        title = element_text(size = 18),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

```

<!-- ## RQ2 (VAR) -->
<!-- ```{r} -->

<!-- # Due to poor quality of fetched comment data, Panel Vector Autoregressive model was impossible to run. -->

<!-- # library(panelvar) -->
<!-- #  -->
<!-- # longitudinal_data_needed <- longitudinal_data_completed %>% -->
<!-- #   mutate( -->
<!-- #     comment_increase = c(sum[1], diff(sum)), -->
<!-- #     polarization_change = c(polarization_score[1], diff(polarization_score)) -->
<!-- #   ) %>% -->
<!-- #   select(username, video_url, time, comment_increase, polarization_change) %>% -->
<!-- #   ungroup() -->
<!-- #  -->
<!-- # longitudinal_data_needed_with_id <- longitudinal_data_needed %>% -->
<!-- #   mutate(video_id = str_split_i(video_url, "/", -1)) %>% -->
<!-- #   data.frame() -->
<!-- #  -->
<!-- # varone <- pvargmm( -->
<!-- #   dependent_vars = c("comment_increase", "polarization_change"), -->
<!-- #   lags = 1, -->
<!-- #   transformation = "fd", -->
<!-- #   data = longitudinal_data_needed_with_id, -->
<!-- #   panel_identifier = c("video_id", "time"), -->
<!-- #   steps = c("twostep"), -->
<!-- #   system_instruments = TRUE, -->
<!-- #   max_instr_dependent_vars = 99, -->
<!-- #   min_instr_dependent_vars = 2L, -->
<!-- #   collapse = FALSE -->
<!-- # ) -->


<!-- ``` -->


## RQ3 (disparagement * partisanship -> engagement, polarization)

### RQ3a disparagement * partisanship -> engagement

```{r}
## num of view
rq3_model_view <- glmmTMB(view_count ~ Disparagement * Partisanship + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_rq3_model_view <- simulateResiduals(rq3_model_view)
# testDispersion(sim_res_rq3_model_view)

## num of likes
rq3_model_like <- glmmTMB(like_count ~ Disparagement * Partisanship + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_rq3_model_like <- simulateResiduals(rq3_model_like)
# testDispersion(sim_res_rq3_model_like)

## num of shares
rq3_model_share <- glmmTMB(share_count ~ Disparagement * Partisanship + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_rq3_model_share <- simulateResiduals(rq3_model_share)
# testDispersion(sim_res_rq3_model_share)

## num of comments
rq3_model_comment <- glmmTMB(comment_count ~ Disparagement * Partisanship + (1 | username), data = df_video, family = nbinom2(link = "log"))
# sim_res_rq3_model_comment <- simulateResiduals(rq3_model_comment)
# testDispersion(sim_res_rq3_model_comment)

# html output of the result
tab_model(rq3_model_view, rq3_model_like, rq3_model_share, rq3_model_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

```

### RQ3b disparagement * partisanship -> polarization

```{r}
## sentiment polarization
rq3_model_polarization <- lmer(polarization_score ~ Disparagement * Partisanship + (1 | username), data = df_video)

tab_model(rq3_model_polarization, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = "Polarization", 
          show.ci = FALSE, 
          show.se = TRUE)

```

### RQ3c disparagement * partisanship * polarization -> engagement

```{r}
## num of view
rq3c_model_view <- glmmTMB(view_count ~ Disparagement * Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of likes
rq3c_model_like <- glmmTMB(like_count ~ Disparagement * Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of shares
rq3c_model_share <- glmmTMB(share_count ~ Disparagement * Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of comments
rq3c_model_comment <- glmmTMB(comment_count ~ Disparagement * Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

tab_model(rq3c_model_view, rq3c_model_like, rq3c_model_share, rq3c_model_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

```

### RQ3c Vizualzation

```{r, fig.width=12, fig.height=6}
figure_for_rq3c <- function(regression_model, fig_num){
  plot_model(
    regression_model,
    type = "pred",
    terms = c("polarization_score", "Disparagement", "Partisanship"),
    line.size = 1.5) +
    aes(linetype = group, colour = group) +
    scale_colour_manual(values = c("Non-disparagement" = "darkgreen", "Disparagement" = "purple")) +
    scale_fill_manual(values = c("Non-disparagement" = "darkgreen", "Disparagement" = "purple")) +
    scale_y_continuous(limits = c(0, NA)) +
    labs(title = fig_num, colour = "Disparagement", linetype = "Disparagement", shape = "Disparagement") +
    theme_minimal()
}

p_rq3c_view <- figure_for_rq3c(rq3c_model_view, "A")
p_rq3c_like <- figure_for_rq3c(rq3c_model_like, "B")
p_rq3c_share <- figure_for_rq3c(rq3c_model_share, "C")
p_rq3c_comment <- figure_for_rq3c(rq3c_model_comment, "D")

(p_rq3c_view + p_rq3c_like + p_rq3c_share + p_rq3c_comment) +
  plot_layout(guides = "collect") &
  theme(legend.position = "right",
        title = element_text(size = 18),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

```

### RQ3c disparagement * partisanship * engagement -> polarization
```{r}
## sentiment polarization, view
rq3c_model_polarization_view <- lmer(polarization_score ~ Disparagement * Partisanship * log10(view_count) + (1 | username), data = df_video)

## sentiment polarization, like
rq3c_model_polarization_like <- lmer(polarization_score ~ Disparagement * Partisanship * log10(like_count) + (1 | username), data = df_video)

## sentiment polarization, share
### log + 1 transformation
rq3c_model_polarization_share <- lmer(polarization_score ~ Disparagement * Partisanship * log10(share_count + 1) + (1 | username), data = df_video)

## sentiment polarization, comment
### log + 1 transformation
rq3c_model_polarization_comment <- lmer(polarization_score ~ Disparagement * Partisanship * log10(comment_count + 1) + (1 | username), data = df_video)

tab_model(rq3c_model_polarization_view, rq3c_model_polarization_like, rq3c_model_polarization_share, rq3c_model_polarization_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = "Polarization", 
          show.ci = FALSE, 
          show.se = TRUE)

```

### RQ3c Post-Hoc analysis

```{r}
## num of view
rq3c_model_view_post <- glmmTMB(view_count ~ Disparagement + Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of likes
rq3c_model_like_post <- glmmTMB(like_count ~ Disparagement + Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of shares
rq3c_model_share_post <- glmmTMB(share_count ~ Disparagement + Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

## num of comments
rq3c_model_comment_post <- glmmTMB(comment_count ~ Disparagement + Partisanship * polarization_score + (1 | username), data = df_video, family = nbinom2(link = "log"))

tab_model(rq3c_model_view_post, rq3c_model_like_post, rq3c_model_share_post, rq3c_model_comment_post, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)


## sentiment polarization, view
post_rq3c_model_polarization_view <- lmer(polarization_score ~ Disparagement + Partisanship * log10(view_count) + (1 | username), data = df_video)

## sentiment polarization, like
post_rq3c_model_polarization_like <- lmer(polarization_score ~ Disparagement + Partisanship * log10(like_count) + (1 | username), data = df_video)

## sentiment polarization, share
### log + 1 transformation
post_rq3c_model_polarization_share <- lmer(polarization_score ~ Disparagement + Partisanship * log10(share_count + 1) + (1 | username), data = df_video)

## sentiment polarization, comment
### log + 1 transformation
post_rq3c_model_polarization_comment <- lmer(polarization_score ~ Disparagement + Partisanship * log10(comment_count + 1) + (1 | username), data = df_video)


tab_model(post_rq3c_model_polarization_view, post_rq3c_model_polarization_like, post_rq3c_model_polarization_share, post_rq3c_model_polarization_comment, 
          transform = NULL, 
          auto.label = TRUE, 
          collapse.ci = FALSE, 
          dv.labels = c("Views", "Likes", "Shares", "Comments"), 
          show.ci = FALSE, 
          show.se = TRUE)

```

### RQ3c Post-Hoc Vizualzation

```{r, fig.width=12, fig.height=6}

figure_for_rq3c_post <- function(regression_model, term, fig_num){
  plot_model(
    regression_model,
    type = "pred",
    terms = c(term, "Partisanship"),
    line.size = 1.5) +
    aes(linetype = group, colour = group) +
    scale_colour_manual(values = c("Democratic" = "blue", "Republican" = "red")) +
    scale_fill_manual(values = c("Democratic" = "blue", "Republican" = "red")) +
    scale_y_continuous(limits = c(0, NA)) +
    labs(title = fig_num, colour = "Partisanship", linetype = "Partisanship", shape = "Partisanship") +
    theme_minimal()
}

p_rq3c_view_post <- figure_for_rq3c_post(rq3c_model_view_post, "polarization_score", "A")
p_rq3c_like_post <- figure_for_rq3c_post(rq3c_model_like_post, "polarization_score", "B")
p_rq3c_share_post <- figure_for_rq3c_post(rq3c_model_share_post, "polarization_score", "C")
p_rq3c_comment_post <- figure_for_rq3c_post(rq3c_model_comment_post, "polarization_score", "D")

(p_rq3c_view_post + p_rq3c_like_post + p_rq3c_share_post + p_rq3c_comment_post) +
  plot_layout(guides = "collect") &
  theme(legend.position = "right",
        title = element_text(size = 18),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

```